Estimating duration in the presence of misclassification

### 2024-03-30 transmission.tex
Overleaf

Specifying $F_Z$ should consider the need to provide structure to stabilise the problem (see \cref{E-intro:sec:disease-model}).
In the context of the CIS, it needs to allow borrowing information across time and/or strata (see \cref{E-biology-data:sec:MRP}), which is required because for some stratum/time combinations the data become very sparse.

>>>>

Specifying $F_Z$ should consider the need to provide structure to stabilise the problem (see \cref{E-intro:sec:disease-model}).
In the context of the CIS, it needs to allow borrowing information across time and/or strata (see \cref{E-biology-data:sec:MRP}).
